---
title: "R Script Documentation"
author: "Harpreet Bhullar"
date: "October 6, 2026"
output: html_document
---

> **AI Assistance Declaration:** I used ChatGPT (GPT-5.6 Sol) on October 6, 2026, for suggestions about Markdown formatting, section organization, and R code-block presentation. I manually reviewed the AI-assisted output and checked the document structure for correctness. No real or personal data was provided to the AI tool. All final work was reviewed by me, and I am responsible for its accuracy and originality.

# Purpose

This R Markdown document describes a simple R script that works with a synthetic sales dataset. The purpose is to demonstrate how an R analysis can be documented clearly using explanatory text, headings, and R code chunks.

Only synthetic data is used in this example.

## Inputs

The script creates a small synthetic dataset containing two variables:

- `month` – identifies the month.
- `sales` – contains a synthetic sales value for each month.

```{r create-data}
project_data <- data.frame(
  month = c("January", "February", "March"),
  sales = c(120, 145, 138)
)```

## View the Data

The following code displays the synthetic dataset.

```{r view-data}
print(project_data)
```

This allows the user to verify that the synthetic dataset was created correctly.

## Data Structure

The `str()` function is used to inspect the structure and data types.

```{r inspect-data}
str(project_data)
```

This helps confirm that the variables have been stored in an appropriate format.

## Summary

The following code produces a basic summary of the dataset.

```{r summary-data}
summary(project_data)
```

The summary provides descriptive information about the variables in the synthetic dataset.

## Outputs

The script produces:

- A synthetic R data frame.
- A printed view of the dataset.
- Information about the structure of the dataset.
- A basic statistical summary.

## Verification

I manually reviewed this R Markdown document to confirm that:

1. The headings follow a clear hierarchy.
2. R code is contained inside valid R Markdown code chunks.
3. The code chunks use R syntax highlighting.
4. Inputs and outputs are clearly explained.
5. Only synthetic data is used.
6. The document is organized for preview or knitting in RStudio or Posit Cloud.

## AI-Assisted Refinement

The following prompts were used:

- "Here's my R script description. Suggest Markdown formatting and code block examples."
- "Add syntax highlighting and improve section organization using Purpose, Inputs, and Outputs."
- "Is the Markdown consistent with RMarkdown best practices?"

After reviewing the suggestions, I improved the organization, kept the explanations concise, and manually checked the R Markdown syntax.

# Conclusion

This document demonstrates how R Markdown can combine R code and explanatory text in one organized document. Clear documentation makes an R project easier to understand, verify, maintain, and share.
